Efficiently summarising relationships in large samples: a general duality between statistics of genealogies and genomes

### 2019-09-02 treestats_paper.tex
removed stuff (closes #7)

%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Acknowledgements}
Thanks to Graham Coop, Andrew Kern, and Kelley Harris for useful suggestions
and to Wilder Wohns and Leo Speidel for providing inferred tree sequences.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Acknowledgements}
Thanks to Graham Coop, Andrew Kern, Nick Patterson, and Kelley Harris for useful suggestions
and to Wilder Wohns and Leo Speidel for providing inferred tree sequences.
